### 2020-02-06 paper/revisions/review-responses.tex

        %--------------------------------------------------------------------
        \question In page 19, why the Pa extraction time was selected to be 30s since Pa is neither the gaseous FPs nor the non-dissolved metals?
        \begin{solution}

        \end{solution}

        %--------------------------------------------------------------------
        \question For Figure 9, it is inaccurate to state that the mass of U-233 reaches equilibrium after ~30 years, apparently from the figure, we can observe that the mass of U-233 for three of the cases still increase/decrease after 30 years.

        \begin{solution}
                Thank you for the excellent point. The statement has been removed from the text.
                Moreover, we rewrite the paragraph to address this thought:\\
                Figure~\ref{fig:U233CC} demonstrates the mass of $^{233}$U in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases. For $^{233}$U case, the mass of $^{233}$U increases with operating time and reaches $\approx$ 1.7 $t$ at the EOL. For reactor-grade Pu and TRU cases, the mass of $^{233}$U firstly, increases and after $\approx$ 35 and 45 years for Pu and TRU cases, respectively, decreases. The neutron spectrum shift during operating affects the inventory of $^{233}$U in the fuel salt. Hard neutron spectrum converts more $^{233}$U from $^{232}$Th. For the reactor-grade Pu and TRU cases, during operating, the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope; the neutron spectrum softens (low conversation of $^{233}$U from $^{232}$Th). However, for $^{233}$U case, the neutron spectrum is hardened at EOL due to the accumulation of Pu isotopes.

### 2020-02-06 paper/results.tex
Comments from Reviewer 2 (6)

Figure~\ref{fig:U233CC} demonstrates the mass of $^{233}$U in the fuel salt 
for the $^{233}$U, reactor-grade Pu, and TRU cases. The mass of 
$^{233}$U reaches equilibrium after $\approx$ $30$ years; overall, the 
amount of $^{233}$U is sufficient to maintain criticality in 
the three cases.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{U233CC.png}
	\caption{Mass of $^{233}$U in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases.}
	\label{fig:U233CC}
\end{figure}

>>>>

Figure~\ref{fig:U233CC} demonstrates the mass of $^{233}$U in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases. For $^{233}$U case, the mass of $^{233}$U increases with operating time and reaches $\approx$ $1.7$ $t$ at the EOL. For reactor-grade Pu and TRU cases, the mass of $^{233}$U firstly, increases and after $\approx$ $35$ and $45$ years for Pu and TRU cases, respectively, decreases. The neutron spectrum shift during operating affects the inventory of $^{233}$U in the fuel salt. Hard neutron spectrum converts more $^{233}$U from $^{232}$Th. For the reactor-grade Pu and TRU cases, during operating, the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope; the neutron spectrum softens (low conversation of $^{233}$U from $^{232}$Th). However, for $^{233}$U case, the neutron spectrum is hardened at EOL due to the accumulation of Pu isotopes.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{U233CC.png}
	\caption{Mass of $^{233}$U in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases.}
	\label{fig:U233CC}
\end{figure}
